Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-11-16 manuscript/manuscript.tex
Normalise tensor and gradient words

The main challenge of the GLQ integration is loss of accuracy when the computation point
gets closer to the tesseroid \citep{Ku1977}.
\citet{Uieda2016} built on the adaptive discretization algorithm of \citet{Li2011}
to automatically obtain integration results with 0.1\% accuracy.
The algorithm consist in recursively splitting the tesseroid into smaller ones when a
threshold is exceeded,
namely when the normalized distance to the computation point is greater than a
``distance-size ratio'' ($D$).
\citet{Uieda2016} have also obtained standard values of $D$
for the gravitational potential, acceleration, and gradient tensor components
by comparing the numerical model with the fields generated by a spherical shell.

@@

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/exponential-delta.pdf}
\caption{
    Numerical error for different exponential density functions and values of the delta
    ratio.
    The top panels show the exponential density functions for different values of $b$
    (Eq. \ref{eq:density-exp}).
    The error computations were performed on the ``Big Grid'' configuration described in
    Table \ref{tab:grids}, with fixed values of the distance-size ratio
    $D$ obtained for the linear density case ($D=1, 2, 8$ for the
    potential, gradient components, and tensor components, respectively).
    The difference is reported as a percentage of the shell values.
    }
\label{fig:delta-exponential}
\end{figure*}

>>>>

The main challenge of the GLQ integration is loss of accuracy when the computation point
gets closer to the tesseroid \citep{Ku1977}.
\citet{Uieda2016} built on the adaptive discretization algorithm of \citet{Li2011}
to automatically obtain integration results with 0.1\% accuracy.
The algorithm consist in recursively splitting the tesseroid into smaller ones when a
threshold is exceeded,
namely when the normalized distance to the computation point is greater than a
``distance-size ratio'' ($D$).
\citet{Uieda2016} have also obtained standard values of $D$
for the gravitational potential, its gradient and Marussi tensor components
by comparing the numerical model with the fields generated by a spherical shell.

@@

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/exponential-delta.pdf}
\caption{
    Numerical error for different exponential density functions and values of the delta
    ratio.
    The top panels show the exponential density functions for different values of $b$
    (Eq. \ref{eq:density-exp}).
    The error computations were performed on the ``Big Grid'' configuration described in
    Table \ref{tab:grids}, with fixed values of the distance-size ratio
    $D$ obtained for the linear density case ($D=1, 2, 8$ for the
    potential, gradient components, and Marussi tensor components, respectively).
    The difference is reported as a percentage of the shell values.
    }
\label{fig:delta-exponential}
\end{figure*}
